{\bf {\Large Improving estimates of ecosystem metabolism by reducing effects of tidal advection on dissolved oxygen time series}}

### 2015-05-24 cover_letter.tex
updated cover letter for resubmission

\documentclass[a4paper,12pt]{article} 
\usepackage{times}
\usepackage[top=1in,bottom=1in,left=1in,right=1in,nohead]{geometry}
\usepackage{graphics}

@@

Enclosed please find our manuscript, entitled `Improving estimates of ecosystem metabolism by reducing effects of tidal advection on dissolved oxygen time series', to be considered as a new method submitted to Limnology and Oceanography: Methods.  Dissolved oxygen time series are commonly used to estimate whole ecosystem metabolism using the `open-water' method.  Application to coastal waters has been problematic because DO time series often reflect variation from biological processes and tidal advection.  Our manuscript describes a statistical model that can greatly reduce the effects of tidal advection on dissolved oxygen time series to improve estimates of ecosystem metabolism.  We describe the theory behind the method and show its application using both simulated and actual DO time series.  Overall, we are confident that this method can effectively reduce the influence of physical advection on metabolism estimates in many cases.  The implications are such that metabolic estimates are more interpretable and there may be increased potential to empirically relate metabolic variation to causal factors at different scales.

All authors have contributed equally to the content of the manuscript and have approved the submitted product.  The manuscript contains only original data and the authors agree to pay publication charges if accepted.  Please note that Dr. Jane Caffrey (University of West Florida) and Dr. Erik Smith (NOAA) have reviewed earlier drafts of the manuscript.  Additionally, we have compiled the manuscript using a \LaTeX\ document preparation system and can provide source files if needed.  We greatly appreciate the opportunity to publish our work in Limnology and Oceanography: Methods.\vspace{0.5in}

>>>>

\documentclass[a4paper,12pt]{article} 
\usepackage{times}
\usepackage[top=1in,bottom=1in,left=1in,right=1in,nohead]{geometry}
\usepackage{graphics}
\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}

@@

\raggedright

Enclosed please find our revised manuscript entitled `Improving estimates of ecosystem metabolism by reducing effects of tidal advection on dissolved oxygen time series'.  We sincerely thank the reviewers and associate editor for providing detailed and insightful comments on our initial draft.  We have made every effort to address these concerns and are hopeful that the revised manuscript is an improvement over the original.  In particular, we have made efforts to more carefully describe appropriate situations for applying the weighted regression approach, additional details describing our methods for estimating open-water metabolism, and more justification for the use of tidal height as a proxy for advection.  We have also created a simple \href{https://github.com/fawda123/WtRegDO}{R package} to accompany the manuscript in response to the request for making the code available.  Our response to the reviewer comments is included as an attachment to this re-submission.

All authors have contributed equally to the content of the revised manuscript and have approved the final product.  The manuscript contains only original data and the authors agree to pay publication charges if accepted.  We greatly appreciate the opportunity to publish our work in Limnology and Oceanography: Methods.\vspace{0.5in}
